R Notebook

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.11.22
UP and at it

getting somewhere

```{r & Clean Data}
      # Drop NA rows
smugCovIdx <- na.omit(smugCovIdx)

@@

#     Extract variables
#####
library(stringr)
          # extract first word of the column, adds values in new Column at the end of DF

@@

# Network: Creating network Data
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()

>>>>

```{r & Clean Data}

  library(stringr)
      # Drop NA rows
smugCovIdx <- na.omit(smugCovIdx)

@@

#     Extract variables
#####

          # extract first word of the column, adds values in new Column at the end of DF

@@

# Network: Creating network Data

## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()
